---
title: "hw2"
output: pdf_document
date: "2024-10-21"
---
# 1. Introduction
The purpose of the survey conducted at the University of California, Berkeley, was to gain a deeper understanding of the gaming habits and preferences of students enrolled in statistics courses during the Fall 1994 semester. By targeting a specific cohort of 314 eligible students from Statistics 2, Section 1, the researchers aimed to gather data on how frequently these students engaged in video gaming and their likes and dislikes related to the activity.

# 2. Analysis
```{r}
#read data
videodata <- read.table("videodata.txt",header =TRUE)
videodata

```




```{r}
#read data
videoMultiple <- read.table("videoMultiple.txt",header = TRUE)
videoMultiple
```

1. 
### Method

```{r}
#find the point estimator
point_estimate_fraction <- sum(videodata$time >0) / length(videodata$time)

confidence_level <- 0.95
z <- qnorm((confidence_level+1)/2)

#find proportion standard error
se <- sqrt(point_estimate_fraction * (1-point_estimate_fraction)) / sqrt(length(videodata))

#find lower and upper confidence interval
lower_interval_estimate_fraction <- point_estimate_fraction - 2 * se
lower_interval_estimate_fraction

higher_interval_estimate_fraction <- point_estimate_fraction + 2*se
higher_interval_estimate_fraction
se
```
### Analysis
We aim to estimate the proportion of students who played video games in the week before the survey using two methods:

The point estimate is 0.37. This is the best single estimate of the proportion based on the sample data. This means that approximately 37% of the students surveyed played a video game in the past week.

With a 95% confidence level, we estimate that the true proportion lies between 0.12 and 0.62. This range accounts for the uncertainty in the estimate, with the standard error being 0.12.

The point estimate provides a specific value, but the interval estimate acknowledges the uncertainty, offering a range where the true proportion is likely to fall.

### Conclusion
The distinction between these two estimates is for understanding the limitations of our inference. While the point estimate provides a single value, it does not account for the inherent variability in sampling. The confidence interval offers a range that acknowledges the uncertainty and gives a more comprehensive picture of where the true proportion likely lies.



2. 
```{r}
# Filter out rows
videodata_clean <- videodata[!is.na(videodata$freq) & videodata$freq != 99, ]

avg_time <- tapply(videodata_clean$time, videodata_clean$freq, mean, na.rm = TRUE)
sd_time <- tapply(videodata_clean$time, videodata_clean$freq, sd, na.rm = TRUE)
count <- table(videodata_clean$freq)

# summary statistics
summary_stats <- data.frame(
    freq = names(avg_time),
    avg_time = as.numeric(avg_time),
    sd_time = as.numeric(sd_time),
    count = as.numeric(count)
)

print(summary_stats)

# Barplot of average time spent per frequency category
barplot(summary_stats$avg_time,
    names.arg = summary_stats$freq,
    main = "Average Time Spent by Reported Frequency",
    xlab = "Reported Frequency of Play",
    ylab = "Average Time Spent (hours)",
    ylim = c(0, max(summary_stats$avg_time, na.rm = TRUE) + 2)
)
```
```{r}
# Boxplot of time spent by frequency category
boxplot(time ~ freq,
    data = videodata_clean,
    main = "Time Spent Playing Video Games by Reported Frequency",
    xlab = "Reported Frequency of Play",
    ylab = "Time Spent (hours)"
)
```
The average time spent by students who reported playing daily was approximately 4.44 hours for the week. This translates to less than 1 hour per day on average, which is low given their self-categorization.

This suggests that the frequency of daily gaming sessions might be short, which may be due to casual gamers (given the dataset was created in 1994, mobile gaming can be reasonably ignored).
The high standard deviation (5.57) implies significant variability, with some daily players playing much longer than others, indicating the presence of outliers or different interpretations of what "daily play" means.

Students who reported playing weekly spent an average of 2.54 hours in the prior week. The standard deviation is also quite high (5.50), indicating a wide range of weekly playtime. The variability could be due to students engaging in longer gaming sessions occasionally but not consistently.

Notably, there are pretty significant outliers in both categories, with the most extreme being a 30 hour playtime for someone in the weekly categorization.

Monthly and Semesterly Players: The averages for these groups are extremely low.

Monthly: 0.056 hours 

Semesterly: 0.043 hours

These figures suggest minimal engagement with video games, aligning with their infrequent gaming habits.

The survey was conducted following a week that included exams, which likely influenced the reported and actual gaming behaviors.

Reduced Gaming Time: An exam week would lead to students to allocate more time to studying. This would likely result in a temporary decrease in gaming time, especially for those who usually play more frequently.

This could explain the low average gaming hours for the "Daily" category, where students, despite reporting daily gaming habits, might have significantly shortened their gaming time during exams.
The exam effect may have impacted the accuracy of the Weekly group as well, reducing the typical number of hours they would have played in a regular week without exams.
Skewed Estimates: The data collected during an atypical exam week might not accurately represent students' normal gaming habits. The extreme outliers may stand out due to average gaming time decreasing. (eg. a few students didn't have exams or didn't care)

Point Estimate Impact: The point estimate for the proportion of students who played video games during the week might be lower than usual due to the reduced engagement during exams.

Confidence Intervals: The confidence intervals calculated in Question 1 may be biased downward, as the variability in playtime could be different in a regular week. The exam week’s reduction in gaming likely compressed the range of playtimes, affecting standard error calculations.



3. 
### Methods
```{r}
#find the point estimator
point_estimate_average <- mean(videodata$time)

confidence_leve <- 0.95
z <- qnorm((1+confidence_level)/2)

#get the variance of data
variance <- 1/length(videodata$time) * sum((videodata$time - point_estimate_average)**2)

#find average standard error
se <- sqrt(variance) / sqrt (length(videodata$time))

#lower and upper 95% confidence interval
lower_interval_estimate_average <- point_estimate_average - 2*se
higher_interval_estimate_average <- point_estimate_average + 2*se

lower_interval_estimate_average
higher_interval_estimate_average
```
### Analysis
The average time spent playing video games in the week prior to the survey is represented by the point estimate of 1.24 hours. This average provides a summary measure of how much time, on average, respondents dedicated to gaming during that week.

The shape of the sample distribution plays a critical role in determining the appropriateness of this interval estimate. If the distribution of the data is approximately normal, the interval estimate is considered reliable. In case the distribution is skewed or exhibits outliers, further examination through a simulation study can help validate the confidence interval. The simulation can assess the robustness of our interval estimate by generating numerous resamples to observe the distribution of sample means and the resulting confidence intervals.

### Conclusion

Overall, this analysis highlights the average gaming habits of students while acknowledging the variability and potential limitations of the data. It underscores the importance of understanding the underlying distribution when making estimates, as this directly affects the reliability of our conclusions. Further validation through simulation could enhance confidence in our interval estimate, ensuring it accurately reflects the true population parameters.



4.
```{r}
reasons_for_likeliness = "Some students may play for social connection, as online multiplayer games allow them to build and maintain friendships. Others might appreciate the creativity that games offer, allowing them to explore virtual worlds, customize characters, or engage in storytelling. Escapism is also a key motivator, as video games provide an immersive experience that can offer a break from everyday stress.
On the flip side, students who dislike gaming might concerns about its impact on physical health, like eye strain or a sedentary lifestyle. Others might feel that games lack a real-life purpose, seeing them as a distraction from more meaningful activities or accomplishments. Addictive behavior is another reason students might dislike games, fearing they could lose control over the time spent gaming. Lastly, some might experience difficulty learning controls, which can make games less enjoyable, especially for casual players. "
```
5.
```{r}
video_data_cleaned <- videodata[!apply(videodata == 99, 1, any),]

like_to_play <- video_data_cleaned[video_data_cleaned$like > 3 ,]
neutral <- video_data_cleaned[video_data_cleaned$like == 3,]
dislike <- video_data_cleaned[video_data_cleaned$like < 3,]

has_pc <- video_data_cleaned[video_data_cleaned$own == 1,]
no_pc <- video_data_cleaned[video_data_cleaned$own == 0,]

male <- video_data_cleaned[video_data_cleaned$sex == 1,]
female <- video_data_cleaned[video_data_cleaned$sex == 0,]

videoMultiple

```


6. 